---
title: "TableRExtracts Introduction"
author: "Justin Ingels"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(TableRExtracts)
library(dplyr)
library(magrittr)
```

# 1 Introduction

The TableRExtracts package is useful for creating table extracts and codebooks
for datasets within R. Table extracts are created as comma-separated value (.csv)
files that provide summary statistics for variables in the dataset. The
benefit of creating extracts is that they can populate tables created in Excel
with dynamic links between the table and the extract (both sheets in Excel).
If something changes with the dataset and the summary statistics need to be 
updated, the table extract can be rerun and replaced in the Excel file and the 
tables will automatically be updated.

This vignette provides an overview for the extract process:
1. Add labels to the variables and values in the dataset
1. Determine the summary statistics of interest
1. Create table extracts
1. Set-up dynamically loaded tables in Excel
1. Copy the extract to the Excel file

# 2 Add Labels

## 2.1 Introduction

We will begin by creating labels for the variables and values in this dataset. 
It is possible to add variable labels one variable at a time. The same is true
of values and value labels which can be added one variable at a time or 
to multiple variables in a single command.

## 2.1.1 Prerequisites

This section will focus on adding labels to the college_grads dataset provided
as part of the TableRExtracts package.

## 2.2.2 college_grads

To explore adding labels to variables and values, we'll use college_grads. This
data frame contains 173 observations corresponding to 173 different majors.
The author of the <fivethirtyeight.com> article, "The Economic Guide to Picking
A College Major" created the dataset using data from the American Community
Survey 2010-2012 Public Use Microdata Series. MOre documentation can be found
in ?college_grads.

```{r}
college_grads
```

```{r}
AddVarLabels(college_grads) <- c("Total" = "Total number of people with major",
                                 "Men" = "Male graduates",
                                 "Women" = "Female graduates")
```


